---
title: "EMCITE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Code for EMCITE algorithm}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The DGPs for Figure 1 in the paper:

| Title of graph             | $X$                        | $Y(0)$      | $\tau$ |
|----------------------------|----------------------------|-------------|--------|
| Y:Linear, ITE:Linear       | Linear                     | Linear      | Linear |
| Y:Linear, ITE:Sin          | Linear                     | Linear      | Sin    |
| Y:Linear, ITE:Square       | Linear                     | Linear      | Square |
| Y:Linear, ITE:Square, p=10 | Linear, with 10 covariates | Linear      | Square |
| Y:Sundin, ITE: Linear      | Linear                     | Sundin      | Linear |
| Y:Sundin, ITE:Square       | Linear                     | Sundin      | Square |
| Y:Zaidi Higher, ITE: Athey | Zaidi Higher               | Zaidi Lower | Athey  |
| Y:Zaidi Lower, ITE: Athey  | Zaidi Lower                | Zaidi Lower | Athey  |
| Y:Lu, ITE: Lu              | Lu                         | Lu          | Lu     |

## Results for IHDP data

| Response Surface | ESS of B-EMCMITE (in \%) |
|:----------------:|:------------------------:|
|     $D G P 3$    |           54.8           |
|     $D G P 2$    |           58.0           |
|     $D G P 4$    |           61.6           |
|     $D G P 7$    |           63.7           |
|     $D G P 1$    |           63.9           |
|     $D G P 8$    |           64.4           |
|     $D G P 6$    |           67.5           |
|     $D G P 5$    |           72.8           |
|    $D G P 10$    |           74.4           |
|     $D G P 9$    |           77.2           |


## Package implementation of EMCITE algorithm


```{r emcite,eval=FALSE}
# Set up python
set.seed(123)
library(emcite)
use_python("/opt/anaconda3/bin/python")
N <- 1000
n1 <- 200
n2 <- 25
td <- dgp(list("N"=N,"p"=4, "covariate"="linear", "y_mean"="linear", "ite"="linear", "real"=F))
s.td <- split_data(td, n1=n1)
m1 <- train_model(s.td[["experimentation"]])
tau.train.preds <- predict_ite(s.td[["experimentation"]], m1)
tau.test.preds  <- predict_ite(s.td[["rollout"]], m1)

thetas <- fit_gradient_descent(X=s.td[["experimentation"]][["X"]],
                               tau_predictions=tau.train.preds$tau, 
                               weight_types = 5)
selections <-
  sapply(c("random", "variance", "type-s", "emcite"), function(x)
    af(
      s.td,
      tau_train = tau.train.preds$tau,
      tau_test = tau.test.preds$tau,
      theta = thetas,
      n2 = n2,
      type = x,
      weight_types = 5,
      parallel = F,R=F
    ), simplify = F, USE.NAMES = T)
```

```{r emcite2,eval=FALSE}
# With assignment function "turned on"
results <- sapply(selections,
                  function(x)
                    retrain_and_metrics(
                      sampling_data(
                        s.td,
                        x,
                        active = T,
                        train_predictions = tau.train.preds,
                        test_predictions   = tau.test.preds
                      )
                    ), 
                       simplify = F, USE.NAMES = T)
res <- rbindlist(results)
res[, selection:=names(selections)]
```
```{r print}
print(res)
```

